Perceptual Symbol Grounding in \\Holographic Memories

### 2016-12-13 papers/hrr-paper/paper.tex
Edit and format abstract

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract}
		Vector Symbolic Architectures (VSA) define a set of operations for association, (compressed) storage, manipulation and retrieval of symbolic concepts, represented as fixed-length vectors from ${\rm I\!R}^N$.
A specific instance of VSA, Holographic Reduced Representations (HRR), has proven to exhibit properties similar to human short-term memory and is, as such, interesting for computational modelling.

		In this paper we extend the HRR approach by introducing implicit, topology-preserving, encoding/decoding procedure using radial basis functions.
Extended approach involves randomly chosen permutation (for encoding) and its inverse (for decoding), necessary for uniform distribution of signal in Fourier space in which embedding takes place.
These novel encoding schemes, together with extended operation pipeline, play the role of so called clean-up modules after memory retrieval (e.g. self-organizing maps).
Effectively, encoding implicitly represents the symbol, so no further lookup is needed.

		We show that this newly introduced encoding scheme didn't have a negative impact on memory capacity in comparison with the original author's capacity benchmark.
We also test our memories in three different robotics tasks: mapping and recall of an area by a mobile agent, top-down visual attention shift and state machine scripting (holographic controllers). 
	\end{abstract}

>>>>

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract}
		Vector Symbolic Architectures (VSAs) define a set of operations
		for association, (compressed) storage, manipulation and retrieval
		of symbolic concepts, represented as fixed-length vectors in
		${\rm I\!R}^N$.
		A subset of VSAs, Holographic Reduced Representations (HRRs),
		have proven to exhibit properties similar to human short-term
		memory and are, as such, interesting for computational modeling.

		In this paper we extend the HRR approach by introducing implicit,
		topology-preserving, encoding/decoding procedures using radial
		basis functions.
		This involves randomly chosen permutations for encoding and
		their corresponding inverse for decoding, which is necessary
		for the uniform distribution of signals in Fourier space where
		embedding takes place.
		These novel encoding schemes, together with the extended operation
		pipeline, are akin to so-called \emph{clean-up modules after memory
		retrieval} (e.g., self-organizing maps). Effectively, encoding
		implicitly represents the symbol, so no further lookup is needed.

		We show that our encoding scheme does not have a negative impact
		on memory capacity in comparison to the original capacity
		benchmark for HRRs by Plate
		\cite{Plate:1995:HolographicReducedRepresentations}.
		We also evaluate our memories in three different robotics tasks:
		mapping and recall of an area by a mobile agent, top-down visual
		attention shift and state machine scripting (holographic
		controllers).
	\end{abstract}
